---
title: "Assignment 1"
author: "Puravasu Jaideep Sesha"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. Data Frame and 4. Data Frame in Markdown

```{r dataframe}
animals <- c("Snake", "Ostrich", "Cat", "Spider")
num_legs <- c(0,2,4,8)
animals_df <- data.frame(animals, num_legs)
animals_df
```

Data types -> animals - chr, num_legs- num

### 2. Check and Delete Objects
```{r check_delete_objects}
ls()
rm(num_legs)
ls()
rm(list = ls())
ls()
```

### 3. R Script Dataframe
```{r script_df}
#### MyFirstRScript.R
animals <- c("Snake", "Ostrich", "Cat", "Spider")
num_legs <- c(0,2,4,8)
animals_df <- data.frame(animals, num_legs)
animals_df
```
source("D:/Bristol Uni/RStudio/R Markdown save spot/Script save spot/myFirstRScript.R")

### 5. Matrix

#### X, Y, Z
```{r matrix}
x_vect <- c(seq(12,2, by = -2))
x_vect
X <- matrix(x_vect, 2, 3)
X
Y <- matrix(seq(4), 2,2)
Y
Z <- matrix(seq(4,10, by=2), 2, 2)
Z
```

#### Transpose
```{r transpose}
t(Y)
t(Z)
```

#### Addition
```{r addition}
Y + Z
Z + Y
```
Matrix addition is 'Commutative'.

#### Multiplication
```{r multiplication}
Y %*% Z
Z %*% Y
```
Matrix multiplication is not commutative.
```{r multiplication2}
Y %*% X
#X %*% Y
```
Error is due to mismatch in order. X is 2(p)x3(q), Y is 2(r)x2(s). For matrix multiplication to work, q should be equal to r.

#### Element-wise multiplication
```{r element_multiplication}
Y * Z
Z * Y
```
Commutative

#### Inverse
```{r inverse}
solve(Y)
Y * solve(Y)
solve(Y) * Y
```
Identity Matrix

### 6. Writing a function
```{r function}
myFirstRFunc <- function(n) {
  if(n<0 || n != as.integer(n) || !is.numeric(n)){
    stop("Invalid! Enter an integer")
  }
  else {
    sum <- 0
    for(i in 1:n-1){
      if(i %% 2 ==0 || i %% 7 == 0){
        sum <- sum + i
      }
    }
  }
  return(sum)
  }
```
myFirstRFunc(14) \
[1] 49 \
myFirstRFunc(1000) \
[1] 284787 \
myFirstRFunc(1.25) \
Error in myFirstRFunc(1.25) : Invalid! Enter an integer